---
title: "week4 presentation"
author: "Jay Panchal"
date: "18/11/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

this application uses `gapminder`and `plotly` package.it shows a plot 
of GDP per capital v/s life expansion.you can select range of year and
visulize the plot.You can get mean,minimum and maximum gdp.





## ui.r and server.r

here are the links for shinyapps.io and github for ui.r and server.r files

-shinyapps.io :<https://jaypanchal.shinyapps.io/week4project/?_ga=2.269205624.866543514.1605691694-26869012.1605691694>

-github:<https://github.com/jaypanc/week4-developing-data-products.git>


## dataset information

Here gapminder dataset is taken.It has six features:country,continent,year,
life expansion,population,gdpPercap.
year starts from 1952 to 2007 with steps of 5 years.

```{r,warning=FALSE,comment=" "}
library(gapminder)
head(gapminder)

```
## plot

```{r,warning=FALSE,message=F,fig.align='center'}
library(plotly)
library(dplyr)
plot_ly(
            data=gapminder,
            x=~gdpPercap,
            y=~lifeExp,
            size = ~pop,
            color = ~continent,
            frame=~year,
            text=~country,
            hoverinfo="text",
            type="scatter",
            mode="markers"
            )%>%
              layout(xaxis=list(type="log"))



```
